%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  
%---------------------------------------------------------
\cventry
{Bimanual Force Control Undergraduate Research} % Job title
{Dr. Martin Barczyk, University of Alberta} % Organization
{Edmonton, Alberta} % Location
{Jan. 2024 - Apr. 2024} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item Worked independently with vague direction
    \item Implemented simple bimanual force control algorithm
    \item Reviewed force control and dynamical systems control literature
    \item Created docker environment for portable development
  \end{cvitems}
}

%---------------------------------------------------------
  \cventry
    {Defence Robotics Research Student} % Job title
    {Defence Research and Development Canada (DRDC)} % Organization
    {Suffield, Alberta Canada} % Location
    {Sept. 2021 - Apr. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Researched LiDAR  Following Algorithm using Machine Learning
        \item Developed Several Following algorithms with varying complexities
        \item Debugged and Augmented a pre-existing Codebase For UGV Autonomous Navigation and Control
        \item Tested Visual Odometry Software
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
{Mechanical Engineering Student} % Job title
{Pegasus Imagery} % Organization
{St. Albert, Alberta Canada} % Location
{Sept. 2022 - Nov. 2023} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item Iterated on a Drone Tail Design with Little Oversight
    \item Manufactured Composite Drone Parts in House
    \item Used a CNC Router to Manufacture Parts as needed
    \item Designed and Modelled FDM printed Parts
    \item Lead the Creation of Build Manuals for Manufacturing Repeatability
  \end{cvitems}
}

%---------------------------------------------------------






\end{cventries}
