%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  
%---------------------------------------------------------
\cventry
{Bimanual Force Control Undergraduate Research} % Job title
{Mechatronic Systems Lab (Dr. Martin Barczyk)} % Organization
{University of Alberta} % Location
{Jan. 2024 - Apr. 2024} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item Implemented simple bimanual force control algorithm
    \item Reviewed force control and dynamical systems control literature
    \item Created docker environment for portable development
    % \item Worked independently with vague direction
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Mechanical Engineering Student} % Job title
{Pegasus Imagery} % Organization
{St. Albert, Alberta Canada} % Location
{Sept. 2022 - Nov. 2023} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item Iterated on a Drone Tail Design with Little Oversight
    \item Manufactured Composite Drone Parts in House
    \item Used a CNC Router to Manufacture Parts as needed
    \item Designed and Modelled FDM printed Parts
    \item Lead the Creation of Build Manuals for Manufacturing Repeatability
  \end{cvitems}
  }
  
  %---------------------------------------------------------
    \cventry
      {Defence Robotics Research Student} % Job title
      {Defence Research and Development Canada (DRDC)} % Organization
      {Suffield, Alberta Canada} % Location
      {Sept. 2021 - Apr. 2022} % Date(s)
      {
        \begin{cvitems} % Description(s) of tasks/responsibilities
          \item Researched LiDAR  Following Algorithm using Machine Learning
          \item Developed Several Following algorithms with varying complexities
          \item Debugged and Augmented a pre-existing Codebase For UGV Autonomous Navigation and Control
          \item Tested Visual Odometry Software
        \end{cvitems}
      }

  %---------------------------------------------------------
\cventry
{Tutor} % Job title
{Tutor} % Organization
{Edmonton, Alberta} % Location
{2020 - 2022} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item Prepared lessons and worked through practice problems
    \item First year engineering calculus, Elementary Math
  \end{cvitems}
}

%---------------------------------------------------------






\end{cventries}
